Global code motion of congruent instructions

### 2017-04-18 paper.tex
fix

Code hoisting opens new opportunities for other hoistable candidates which were
of higher rank (depended on candidates which got hoisted). Ideally we could
iterate on lower ranking expressions first and then proceed to higher ranking
expressions in the same iteration but \LLVM{'}s \GVN{} infrastucture does not
compute equivalence classes in a effective way. We found it simpler to just
recompute the value numbers and start finding hoistable candidates again.

>>>>

Code hoisting opens new opportunities for other hoistable candidates which were
of higher rank (depended on candidates which got hoisted). Ideally we could
iterate on lower ranking expressions first and then proceed to higher ranking
expressions in the same iteration but \LLVM{'}s \GVN{} infrastucture does not
compute equivalence classes in an effective way. We found it simpler to just
recompute the value numbers and start finding hoistable candidates again.
